---
title: "Results Section Three: Cooccurrence and Bigrams"
description: "Project description here"
tags: ["R", "networks"]
weight: 4
draft: false
output: html_document
---

[Here you will describe the data discoversy process, the data used, and the methods employed for this single page. Since you already have a Project Overview and Data & Methods tabs, you probably want to keep this first paragraph fairly short and use the rest of the document to walk your readers through your analyses.] 

```{r setup, include=FALSE}
#libraries
library(tidytext)
library(data.table)
library("RPostgreSQL")
library(stringi)
library(textstem)
library(dplyr)
library(tidyr)
library(SnowballC)
library(igraph)
library(ggraph)
library(widyr)
library(stringr)
```

```{r functions, include = FALSE}
# Visualizing Bigrams functions
# From tidytext documentation
visualize_bigrams <- function(bigrams, title) {
  set.seed(2020)
  a <- grid::arrow(type = "closed", length = unit(.15, "inches"))
  
  bigrams %>%
    graph_from_data_frame() %>%
    ggraph(layout = "fr") +
    geom_edge_link(aes(edge_alpha = n), show.legend = FALSE, arrow = a) +
    geom_node_point(color = "lightblue", size = 5) +
    geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
    theme_void() + theme(legend.position = "none",
                      plot.title = element_text(hjust = 0.5)) +
    ggtitle(title)
}

cooccur_gender <- function(data, dictionary, n=5, corr=.15){
  
  data %>%
  mutate(section = row_number()) %>%
  filter(section > 0) %>%
  unnest_tokens(word, text) %>%
  filter(!word %in% stop_words$word) %>%
  mutate(word = stem_words(lemmatize_words(word))) %>%
  group_by(word) %>% 
  filter(n() >= n) %>%
  pairwise_cor(word, section, sort = TRUE) %>%
  filter(grepl(dictionary, item1))%>%
  filter(correlation >= corr) 
}
visualize_cooccur <- function(data, title){
  set.seed(2020)
  data %>%
  graph_from_data_frame() %>%
  ggraph(layout = "fr") +
  geom_edge_link(aes(edge_alpha = correlation), show.legend = FALSE) +
  geom_node_point(color = "lightblue", size = 5) +
  geom_node_text(aes(label = name), repel = TRUE) +
  theme_void() + ggtitle(title)
}

```

```{r dataload, include = FALSE}
conn <- dbConnect(drv = PostgreSQL(),
                  dbname = "sdad",
                  host = "10.250.124.195",
                  port = 5432,
                  user = Sys.getenv("db_userid"),
                  password = Sys.getenv("db_pwd"))
# query the bipartite edgelist data from github data
data <- dbGetQuery(conn, "SELECT * FROM american_soldier.survey_32_clean")
dbDisconnect(conn)

##### some data cleaning
#remove possessive 's
data$outfits_comment <- str_replace_all(data$outfits_comment, "'s", "")
data$long <- str_replace_all(data$long, "'s", "")

data$outfits_comment <- str_replace_all(data$outfits_comment, "\\+", "and")
data$long <- str_replace_all(data$long, "\\+", "and")

#remove all symbols except periods.
data$outfits_comment <- str_replace_all(data$outfits_comment, "[^[:alnum:][:space:].]", "")
data$long <- str_replace_all(data$long, "[^[:alnum:][:space:].]", "")

collapse <- fread("~/git/dspg2020amsoldier/data/dictionary/collapse_words.csv", sep = ",") 
collapse <- mutate(collapse, original = paste("\\b", original,"\\b", sep = "")) #so that stringr doesn't pick up on instances where it is part of another word

#make sure replace with collapsed words
data$long <- stri_replace_all_regex(data$long, collapse$original, collapse$collapse, vectorize_all = FALSE)
data$outfits_comment <- stri_replace_all_regex(data$outfits_comment, collapse$original, collapse$collapse, vectorize_all = FALSE)

#### create custom stop words 
custom_stop <- append(stop_words$word, c("question", "questionnaire", "answer"))
```

# How do Black and White soldiers talk about gender roles?
In addition to analyzing race relations between soldiers, we want to see how gender roles were discussed amongst soldiers. Our particular focus is on women's gender roles during the time of 1943 and at the intersection of race relations.

A dictionary of gender words are loaded to identy which responses relate to gender topics. 
```{r dictionaryload}
#load dictionary csv
gender_words <- fread("~/git/dspg2020amsoldier/data/dictionary/gender.csv", sep = ",");head(gender_words) 
gender_match <- paste(paste("\\b", gender_words$gender,"\\b", sep = ""), collapse="|") #regex friendly 
```

```{r data_subset, include = FALSE}
#subset data on quesiton
S32_short <- data %>% select(outfits_comment) %>% filter(!is.na(outfits_comment))
S32_short <- tibble(nrow=1:nrow(S32_short), text = S32_short$outfits_comment)

S32_long <- data %>% select(long) %>% filter(!is.na(long))
S32_long <- tibble(nrow=1:nrow(S32_long), text = S32_long$long)


#subset data based on question and race
S32W_short <- data %>% filter(racial_group== "white") %>% select(outfits_comment) %>% filter(!is.na(outfits_comment))
S32W_short <- tibble(nrow=1:nrow(S32W_short), text = S32W_short$outfits_comment)

S32W_long <- data %>% filter(racial_group== "white") %>% select(long) %>% filter(!is.na(long))
S32W_long <- tibble(nrow=1:nrow(S32W_long), text = S32W_long$long)

S32N_long <- data %>% filter(racial_group== "black") %>% select(long) %>% filter(!is.na(long))
S32N_long <- tibble(nrow=1:nrow(S32N_long), text = S32N_long$long)

```


### Main Findings 

#### Which words do soldiers use to pair with female relating words? 
In the long response question, soldiers are asked to give their feedback on any part of the questionnaire. Any and all aspects of the war were free to talk about. 
```{r echo = FALSE}
female_words <- gender_words %>% filter(category == "female" | category == "relation") %>% add_row(gender = "like", category = "relation")
female_match <- paste(paste("\\b", female_words$gender,"\\b", sep = ""), collapse="|") #regex friendly 
keep_female <- append(gender_words$gender, c("coloredsoldi", "negrosoldi", "white", "negro"))


S32_long <- data %>% select(long) %>% filter(!is.na(long))
S32_long <- tibble(nrow=1:nrow(S32_long), text = S32_long$long)

long_bigrams_female <- S32_long %>% unnest_tokens(bigram, text, token = "ngrams", n=2) %>% 
  count(bigram, sort =TRUE) %>% filter(grepl(female_match, bigram)) %>%
  separate(bigram, c("word1", "word2"), sep = " ") %>%
  filter(!word1 %in% filter(stop_words, word != "like" & word != "with" & word != "liked")$word) %>%
  filter(!word2 %in% filter(stop_words, word != "like" & word != "with" & word != "liked")$word)  %>% 
  mutate(word1 = textstem::lemmatize_words(word1), word2 = textstem::lemmatize_words(word2)) %>%
  mutate(word1 = wordStem(word1), word2 = wordStem(word2)) %>%
  count(word1, word2, sort = TRUE) 
long_bigrams_female <- long_bigrams_female[!(long_bigrams_female$word1 == "like" & !long_bigrams_female$word2 %in% keep_female),]
long_bigrams_female <- long_bigrams_female[!(long_bigrams_female$word2 == "like" & !long_bigrams_female$word1 %in% keep_female),]

visualize_bigrams(long_bigrams_female, "Soldiers' Long Response - Female Words Bigrams")
```

We can see at the like node there is a chain of "whiteman like colorwoman." There are also instances of whiteman are like black men/soldiers. This is either relating the two in similarity or in emotion of likeness between the two.

Another interesting addition to the network with relationship words is the chain of bigrams "sex intercourse with whitewoman". A hot topic was white soldiers being concerned with black soldiers having sexual relations with 'their' whitewomen. Likewise, black soldiers were aware of the tension of being falsely accused for raping or having sex with white women.

Otherwise, themes of family are prevelant for women's role in the commentary of the soldiers. We can also see the different pairings with the word woman, seeming to talk about their roles as workers amongst other attributes  (worker, waac, auxiliary)


Lets see how these pairings differ between the white and black soldiers:
```{r echo = FALSE}
female_words <- gender_words %>% filter(category == "female" | category == "relation") %>% add_row(gender = "like", category = "relation")
female_match <- paste(paste("\\b", female_words$gender,"\\b", sep = ""), collapse="|") #regex friendly 
keep_female <- append(gender_words$gender, c("coloredsoldi", "negrosoldi", "white", "negro"))


S32N_long <- data %>% select(racial_group,long) %>% filter(!is.na(long), racial_group == "black")
S32N_long <- tibble(nrow=1:nrow(S32N_long), text = S32N_long$long)

long_bigrams_female <- S32N_long %>% unnest_tokens(bigram, text, token = "ngrams", n=2) %>% 
  count(bigram, sort =TRUE) %>% filter(grepl(female_match, bigram)) %>%
  separate(bigram, c("word1", "word2"), sep = " ") %>%
  filter(!word1 %in% filter(stop_words, word != "like" & word != "with" & word != "liked")$word) %>%
  filter(!word2 %in% filter(stop_words, word != "like" & word != "with" & word != "liked")$word)  %>% 
  mutate(word1 = textstem::lemmatize_words(word1), word2 = textstem::lemmatize_words(word2)) %>%
  mutate(word1 = wordStem(word1), word2 = wordStem(word2)) %>%
  count(word1, word2, sort = TRUE) 
long_bigrams_female <- long_bigrams_female[!(long_bigrams_female$word1 == "like" & !long_bigrams_female$word2 %in% keep_female),]
long_bigrams_female <- long_bigrams_female[!(long_bigrams_female$word2 == "like" & !long_bigrams_female$word1 %in% keep_female),]

visualize_bigrams(long_bigrams_female, "Black Soldiers' Long Response - Female Words Bigrams")
```

  

```{r echo = FALSE}
female_words <- gender_words %>% filter(category == "female" | category == "relation") %>% add_row(gender = "like", category = "relation")
female_match <- paste(paste("\\b", female_words$gender,"\\b", sep = ""), collapse="|") #regex friendly 
keep_female <- append(gender_words$gender, c("coloredsoldi", "negrosoldi", "white", "negro"))


S32W_long <- data %>% select(racial_group,long) %>% filter(!is.na(long), racial_group == "white")
S32W_long <- tibble(nrow=1:nrow(S32W_long), text = S32W_long$long)

long_bigrams_female <- S32W_long %>% unnest_tokens(bigram, text, token = "ngrams", n=2) %>% 
  count(bigram, sort =TRUE) %>% filter(grepl(female_match, bigram)) %>%
  separate(bigram, c("word1", "word2"), sep = " ") %>%
  filter(!word1 %in% filter(stop_words, word != "like" & word != "with" & word != "liked")$word) %>%
  filter(!word2 %in% filter(stop_words, word != "like" & word != "with" & word != "liked")$word)  %>% 
  mutate(word1 = textstem::lemmatize_words(word1), word2 = textstem::lemmatize_words(word2)) %>%
  mutate(word1 = wordStem(word1), word2 = wordStem(word2)) %>%
  count(word1, word2, sort = TRUE) 
long_bigrams_female <- long_bigrams_female[!(long_bigrams_female$word1 == "like" & !long_bigrams_female$word2 %in% keep_female),]
long_bigrams_female <- long_bigrams_female[!(long_bigrams_female$word2 == "like" & !long_bigrams_female$word1 %in% keep_female),]

visualize_bigrams(long_bigrams_female, "White Soldiers' Long Response - Female Words Bigrams")
```

We see a complete lack of narrative in black women specifically. Conversations about women are mostly about their role in the family as a mother, wife or sister. Another common conversation is about working women, with pairings to WAAC, auxiliary (referring to WAAC) and worker.




#### Which words that soldiers use are correlated with female relating words?
An alternative to the method of bigrams, Co-occurrences measure the correlation of two words appearing with one another in a body of text. Unlike bigrams, these words do not have to appear directly next to one another, and their strength of association is measured.


First, we will look at which words are correlated with female words in all soldiers' long responses.   
```{r echo = FALSE}
female_words <- gender_words %>% filter(category == "female" | category == "relation") %>% add_row(gender = "like", category = "relation")
female_match <- paste(paste("\\b", female_words$gender,"\\b", sep = ""), collapse="|")

long_fem_co <- cooccur_gender(S32_long, female_match, n=5, corr=.12)
long_fem_co <- long_fem_co[!(long_fem_co$item1 == "like" & !long_fem_co$item2 %in% keep_female),]
long_fem_co <- long_fem_co[!(long_fem_co$item2 == "like" & !long_fem_co$item1 %in% keep_female),]

visualize_cooccur(long_fem_co, "Female related co-occurrences for long soldier response")
```



Themes of family are still prevelant. Negrowoman are associated with some negative words like filthy and invade. Whitewomen associations with the words intercourse, cry and molest are related to the controversy of black men having sexual realtions with whitemen. In addition, whitewomen is associated with negroman. This is shows that there is commentary of the association of black and white women which was controversial at the time. 


Next, we will break it down by race.   

```{r echo = FALSE}
female_words <- gender_words %>% filter(category == "female" | category == "relation") %>% add_row(gender = "like", category = "relation")
female_match <- paste(paste("\\b", female_words$gender,"\\b", sep = ""), collapse="|")

long_fem_co <- cooccur_gender(S32N_long, female_match, n=5, corr=.12)
long_fem_co <- long_fem_co[!(long_fem_co$item1 == "like" & !long_fem_co$item2 %in% keep_female),]
long_fem_co <- long_fem_co[!(long_fem_co$item2 == "like" & !long_fem_co$item1 %in% keep_female),]

visualize_cooccur(long_fem_co, "Female related co-occurrences for long Black soldiers' responses")
```



One of the strongest correlations are between negrowoman and negroman as well as negroman and whitewoman. This is indicative that interracial relations are one the most heavily correlated topics to women in the Black soldiers' responses. 
In addition, mother, sister and father have some of the strongest correlations, showing that women's most prevalent role for the soldiers was in their families.     



```{r echo= FALSE}
female_words <- gender_words %>% filter(category == "female" | category == "relation") %>% add_row(gender = "like", category = "relation")
female_match <- paste(paste("\\b", female_words$gender,"\\b", sep = ""), collapse="|")

long_fem_co <- cooccur_gender(S32W_long, female_match, n=5, corr=.15)
long_fem_co <- long_fem_co[!(long_fem_co$item1 == "like" & !long_fem_co$item2 %in% keep_female),]
long_fem_co <- long_fem_co[!(long_fem_co$item2 == "like" & !long_fem_co$item1 %in% keep_female),]

visualize_cooccur(long_fem_co, "Female related co-occurrences for long White soldiers' responses")
```


These words correlated with female words seem inherently random. This could be due to the fact that commentary about women were included in responses that talked about other various topics regarding the war and soldier life. However, we again see an absence of discussion about Black women as a whole. 


### Conclusion and Policy Implications 

[Here you could highlight the main takeaways and the potential policy implications of your findings.] 

### References 

[List your references here using APA format (or at least standardize all of the references using the same format).]